IRT procedures for shortening tests

### 2024-10-10 the-good-the-bad-the-ugly.qmd
upd
mmm

---
title: "IRT procedures for shortening tests"
author: "Ottavia M. Epifania & Friends"
format: 
  revealjs: 
    theme: mytheme.scss
    logo: "www/psicostat.jpg"
    footer: "Psicostat meeting"
background-opacity: "0.45"
title-slide-attributes: 
   data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
   data-background-size: 450px, cover
   data-background-position: 50% 15%, center
server: shiny
---

@@

 sliderInput("b1", "b1",
                  min = -3, max = 3,
                  value = 0, step = 0.1)
sliderInput("b2", "b2",
                  min = -3, max = 3,
                  value = 0, step = 0.1)
sliderInput("b3", "b3",
                  min = -3, max = 3,
                  value = 0, step = 0.1)

sliderInput("a1", "a1",
                  min = 0.20, max = 3,
                  value = 1, step = 0.1)
sliderInput("a2", "a2",
                  min = 0, max = 3,
                  value = 0.70, step = 0.1)
sliderInput("a3", "a3",
                  min = 0, max = 3,
                  value = 1.90, step = 0.1)
checkboxInput("showTif", "Show Test Information Function", value = FALSE)

@@

At $k =0$, $TIF^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate

@@

2. $\forall i \in A^k$, $PIF_{i}^k = \frac{TIF^k + IIF_{i}}{||Q^k||+1}$

3. $D = \arg \min_{i \in A^k} |TIF^* - PIF_i^k|$

Termination criterion: $|TIF^* - PIF_D^{k}| \geq |TIF^* - TIF^{k-1}|$:

>>>>

---
title: "IRT procedures for shortening tests"
author: "Ottavia M. Epifania & Friends"
format: 
  revealjs: 
    theme: mytheme.scss
    logo: "www/psicostat.jpg"
    footer: "Psicostat meeting"
background-opacity: "0.45"
title-slide-attributes: 
   data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
   data-background-size: 400px, cover
   data-background-position: 50% 10%, center
server: shiny
---

@@

 sliderInput("b1", "b1",
                  min = -3, max = 3,
                  value = 0, step = 0.1)
sliderInput("b2", "b2",
                  min = -3, max = 3,
                  value = -1, step = 0.1)
sliderInput("b3", "b3",
                  min = -3, max = 3,
                  value = 1, step = 0.1)

sliderInput("a1", "a1",
                  min = 0.20, max = 3,
                  value = 1, step = 0.1)
sliderInput("a2", "a2",
                  min = 0, max = 3,
                  value = 1, step = 0.1)
sliderInput("a3", "a3",
                  min = 0, max = 3,
                  value = 1, step = 0.1)
checkboxInput("showTif", "Show Test Information Function", value = FALSE)

@@

At $k =0$, $\mathbf{TIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate

@@

2. $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$

3. $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$

Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$:
